The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
reflow

Within each layer, we assumed individuals were
associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
other) were within a given distance of one another. Typically for ungulates and
other gregarious mammals, the ‘chain rule’ is applied for group assignment. For
GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes
buffered by a given distance formed a contiguous buffer for two or more
individuals, even if some individuals within the buffer were not within the
given distance of one another [@Robitaille_2019]. Group assignment based
on the chain rule has previously been applied to caribou at a distance of 50m
[@Peignier_2019; @Lesmerises_2018]. In all networks, nodes
represented individuals, intralayer edges represented associations between
individuals in a given habitat type and season, and interlayer edges represented
connections between the same individuals across contexts.

>>>>

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes (i.e., recorded within 5 minutes of each other) were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts.
